---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path=FALSE)
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```


# Summary

The code could re-run successfully.

Key challenges: (1) dataset required is large and access is provided on
request rather than being freely available on the internet. (2)
significant number of R packages to install -- but all are available
and so just requires some time to set up, together with corresponding
unix binaries.

## Questions


1. Key figures from the manuscript (figures 5--7) are not directly
output from R, so could not be regenerated directly.  Is there an easy
way for them to be regenerated (even just the core data, not
necessarily with all the extra markup and context)?  I have included
Rplots.pdf in case any of those plots relate to the plots in the
paper.  (Click on the name in the table to see the file online.)

2. Do either of you have orcids?

3. See some minor problems below with Table 3.

4. Could Table 1 easily be regenerated?  I couldn't see it being
generated by the R code.


# CODECHECKER notes

The GitHub repo was
<https://github.com/codecheckers/GWR-in-educational-planning>


## Installation prerequisites

A file `codecheck/installs.R` was created to do the local
installations.  Some of the R packages required extra linux packages
to be installed, notably 'gdal' and 'udunits' -- see the R script for
details.  The installation required many R packages, taking about 20
minutes to install.  This was non-trivial to setup, and perhaps in
future could benefit from a Docker container.



## Data 

The data required for the project is not publicly available, but is
available upon request (note procedure in github file).  The file
`Replication files.zip` is 867 Mb.  This zip file was unpacked and
stored in a separate directory to the github.

As the main R script was quite long, I created a symlink to the file

```
ln -s "Geographically weighted regressions for prioritizing educational planning, policies, and interventions - Supporting code.r" code.R
```

Inside `code.R`, I set the variable 

```
replication.folder = "/home/stephen/archive/proj/2022/gwr/Replication files"
```

## Changes to the code.

Only minor changes to the code were required.  I used `file.path()`
rather than assuming the directory separator is `\\` (as it is on
Windows). I also added the followin line to the end of the R script so
that it reports the packages used in the R at the end of code.Rout:

```{r, eval=FALSE}
sessionInfo()
```


## Running the code

To run the code:

```
R CMD BATCH code.R
```

I then used a script, `running.sh`, to copy key outputs across from
the directory where code was run into the codecheck repo.  The code
took just over an hour to run.  I have stored the `Rplots.pdf`  and
`code.Rout` output from the run into the results directory.


\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}

\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:2,"comment"]}
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
```

\clearpage

## Table 2

Table 2 was reproducible.  During the review, code was provided to output
the data for the table, which I have saved into a CSV and rendered
here (using the  slightly different column headings from the CSV).

```{r}
tab2raw <- read.csv("results/table2.csv")
keep <- c("X", "mean", "std.dev", "median", "min", "max")
tab2 <- tab2raw[,keep]
```

```{r, results='asis',echo=FALSE}
print(xtable(tab2, caption="Reproduction of Table 2.",
             digits=2),
      format.args = list(big.mark = ","),
      comment=FALSE, booktabs=TRUE,
      include.rownames=FALSE)
```


## Table 3

Table 3 was reproducible.  The .csv file underlying the outputs was
saved into the `Replication files/Tables/` directory.  This can be
read into R and rendered.

```{r}
tab3 <- read.csv("results/table3.csv")
stars <- rep("", nrow(tab3))
p <- tab3$p.value

## order important here -- do least significant first.
if (any(sig <- (p < 0.1) ))   stars[sig] <- "*"
if (any(sig <- (p < 0.05) ))   stars[sig] <- "**"
if (any(sig <- (p < 0.01) ))   stars[sig] <- "***"
tab3$significance <- stars

## rearrange the rows to match the paper
reorder <- c(2, 14, 15, 12, 5, 7, 6, 8, 4, 13, 9, 10, 11, 3, 1)

tab3_neat <- tab3[reorder, c(2, 3, 4, 7)]
```

```{r, results='asis',echo=FALSE}
print(xtable(tab3_neat, caption="Reproduction of Table 3.",
             digits=-3),
      comment=FALSE, booktabs=TRUE,
      include.rownames=FALSE)
```


The R-squared value at the bottom of Table 3 in the manuscript is
confirmed in the .Rout file (line 541).  The number of observations can be
derived from 1055 d.f. with 14 variables.

There are however two minor problems with the table:

1. *Threat* has one star in the manuscript, yet it should have two
stars according to the legend.
2. *TransEducP* in the manuscript is missing the exponent; the values
in Table C1 match the output from the .Rout (5.273e-07,  1.091e-06)
line 532.


## Acknowledgements



# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
